Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
stuff
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\usepackage{graphicx}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{pstricks}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System Built on Ceph},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

@@

@@

@@

\subsection{Mantle: A Programmable Metadata Load
Balancer}\label{mantle-a-programmable-metadata-load-balancer}

@@

>>>>

\usepackage{graphicx}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{pstricks}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System Built on Ceph},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

@@

% todo:
%  - ellude to the need for policies to be avialable quickly to support
%    our experiment about propogtation delay
%

@@

% todo:
%  - ellude to the need for interfaces to be avialable quickly to support
%    our experiment about propogtation delay
%

@@

\subsection{Mantle: A Programmable Metadata Load Balancer}

@@

The second service implemented on Malacology is ZLog, and a high-performance
distributed shared-log that is based on the CORFU protocol~\cite{corfu}. A
shared-log is a general, yet powerful abstraction used to build many
distributed systems. However, existing implementations that rely on consensus
algorithms such as PAXOS funnel I/O through a single point introducing a
bottleneck that restricts throughput. In contrast, the CORFU protocol is able
to achieve high throughput using a \emph{volatile} in-memory network counter
service (called a \emph{sequencer}) that distributes log positions to clients,
and may run at very high rates. Failures in CORFU are handled by a recovery
algorithm that recomputes the sequencer state using custom storage interfaces
to discover the tail of the log.

A full dexription ...

that computes the
tail of the log by contacting each storage device

Two i

The CORFU protocol handles failures using a combination of

Failures in CORFU are handled using a recovery protocol that res
